SPARQL on the Open, Decentralised Web

### 2016-11-17 dissertation/index.tex
scaling the papers, fixes #23

\includepdf[pages=1-last,openright]{/home/kjetil/uio/www_docs/2012/hypermedia-rdf.pdf}
\includepdf[pages=1-last,openright]{/home/kjetil/uio/www_docs/2013/iswc.pdf}
\includepdf[pages=1-last,openright]{paper14.pdf}
\includepdf[pages=1-last,openright]{/home/kjetil/uio/www_docs/2015/cache-survey.pdf}
\includepdf[pages=1-last,openright]{report.pdf}
\includepdf[pages=1-last,openright]{noise.pdf}
\end{document}

>>>>

\includepdf[pages=1-last,openright,scale=1.2]{/home/kjetil/uio/www_docs/2012/hypermedia-rdf.pdf}
\includepdf[pages=1-last,openright,scale=1.2]{/home/kjetil/uio/www_docs/2013/iswc.pdf}
\includepdf[pages=1-last,openright,scale=1.2]{paper14.pdf}
\includepdf[pages=1-last,openright,scale=1.2]{/home/kjetil/uio/www_docs/2015/cache-survey.pdf}
\includepdf[pages=1-last,openright]{report.pdf}
\includepdf[pages=1-last,openright,scale=1.2]{noise.pdf}
\end{document}
